### 2017-11-15 paper/sections/1_introduction.tex
paper: addresses #22
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches extensively to improve performance
and resource utilization but the policies that guide what data to evict and
when to evict vary with the application or use case. For example, caching file
system metadata on both clients and servers reduces the number of remote
procedure calls and drastically improves the performance of create-heavy
workloads common in HPC~\cite{ren:sc2014-indexfs, patil:fast2011-giga+}. But
these techniques are specific to the domain and application's behavior and a
new use case may prove to be poor a match for the selected caching
policy~\cite{sevilla:sc15-mantle, weil:sc2004-dyn-metadata,
weil:osdi2006-ceph}. In this paper, we evaluate a variety of caching policies
using a general framework that supports policy switching and arrive at a
customized policy that works well for our target application and storage
system.  Trying general policies and iterating to a very customized solution
confirms that our prototype can adapt to different types of workloads; but more
importantly, this is the second system and domain that we have successfully used
this policy language and engine in. This breadth helps us reason about more
general data management policies by giving us a framework to compare and
contrast policies from other domains and services.

>>>>

Storage systems use software-based caches extensively to improve performance
and resource utilization but the policies that guide what data to evict and
when to evict vary with the application or use case. For example, caching file
system metadata on both clients and servers reduces the number of remote
procedure calls and drastically improves the performance of create-heavy
workloads common in HPC~\cite{ren:sc2014-indexfs, patil:fast2011-giga+}. But
these techniques are specific to the domain and application's behavior and a
new use case may prove to be poor a match for the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using a general framework that supports policy
switching and arrive at a customized policy that works well for our target
application and storage system.  Trying general policies and iterating to a
very customized solution confirms that our prototype can adapt to different
types of workloads; but more importantly, this is the second system and domain
that we have successfully used this policy language and engine in. This breadth
helps us reason about more general data management policies by giving us a
framework to compare and contrast policies from other domains and services.
